On the Functionality of the Multilayer Perceptron

### 2020-11-16 Thesis/Drafts/Buell-PHYS799-ThesisDraft0.tex
Updates to thesis & figures

@@

\paragraph*{}Preprocessing a data set is a necessary step to execute prior to feature extraction \cite{Geron2,James}. In the case of audio files, preprocessing usually consists of ensuring that the data set contains the following:
\begin{enumerate}
\item A suitably sized number of files, of reasonable audio quality, with normalized amplitudes
\item Audio encoded in a standard, and consistent format
\item A consistent sample rate and bit depth between audio files
\item A consistent number of channels
\end{enumerate}
Note that different projects may require a different set of requirement from preprocessing \cite{Virtanen}. For this project, we have chosen to use the following parameters:
\begin{enumerate}
\item Roughly $16,000$ audio files Professionally or semi-professionally recorded in a studio. \textcolor{red}{Citation needed!}. All ampltiudes have been normalized to $\pm 1$ unit.
\item All audio has be converted into \textit{.WAV} files from other formats, such as \textit{.AIF} or \textit{.MP3} using a MATLAB program
\item All audio is sampled at $44,100$ Hz and \textcolor{blue}{Bit depth needed - 16? 24?}
\item All audio has been down-mixed into mono-channel waveforms.
\end{enumerate}

@@

\begin{figure}[H]
\begin{center}
\textcolor{red}{Plot of TDE Feature Here}
%\includegraphics[scale=0.3]{../FiguresFeatures/Time_Domain_Env}
\end{center}
\caption{A comparison of the Time Domain Envelope across each class using a box-and-whisker plot}
\label{fig-FeatureTDE}
\end{figure}

@@

\begin{figure}[H]
\begin{center}
\textcolor{red}{PLOT OF ZXR FEATURES HERE}
\end{center}
\caption{A comparison of the Zero-Crossing Rate for each class using a box-and-whisker plot}
\label{fig-FeatureZXR}
\end{figure}

@@

\begin{figure}[H]
\begin{center}
\textcolor{red}{PLOT OF TCM FEATURES HERE}
\end{center}
\caption{A comparison of the temporal center mass for each class using a box-and-whisker plot}
\label{fig-FeatureTCM}
\end{figure}

@@

\begin{figure}[H]
\begin{center}
\textcolor{red}{PLOT OF ACC FEATURES HERE}
\end{center}
\caption{A comparison of the the first four auto correlation coefficents in each class using a box-and-whisker plot}
\label{fig-FeatureACC}
\end{figure}

@@

\paragraph*{}As the frequency bin index increases, the width of the bin in frequency space increases. For instruments with higher fundamental frequencies, we expect very little energy in the lower frequency bins, and also a lower MFCC value. For instruments with lower fundamental frequencies, we expected

\begin{figure}[H]
\begin{center}
\textcolor{red}{PLOT OF MFCC FEATURES HERE}
\end{center}
\caption{A comparison of the $12$ Mel Frequency Cepstral Coefficients for each class using box-and-whisker plots}
\label{fig-FeatureMFCCs}
\end{figure}

@@

\begin{figure}[H]
\label{fig-FeatureFCM}
\begin{center}
\textcolor{red}{PLOT OF FCM FEATURES HERE}
\end{center}
\caption{Frequency center-of-mass visualized in feature-space}
\end{figure}

>>>>

\textcolor{red}{Describe nature of features w/ separation boundaries}

@@

\paragraph*{}Preprocessing a data set is a necessary step to execute prior to feature extraction \cite{Geron2,James}. In the case of audio files, preprocessing usually consists of ensuring that the data set contains the following steps and requirements:
\begin{enumerate}
\item A suitably sized number of files of reasonable audio quality with normalized amplitudes
\item Audio encoded in a standard, and consistent format
\item A consistent sample rate and bit depth between audio files
\item A consistent number of channels
\end{enumerate}
Note that different projects may require a different set of requirement from preprocessing \cite{Virtanen}. For this project, we have chosen to use the following parameters:
\begin{enumerate}
\item Roughly $18,000$ audio files Professionally or semi-professionally recorded in a studio. \textcolor{red}{Citation needed!}. All ampltiudes have been normalized to $\pm 1$ unit.
\item All audio has be converted into \textit{.WAV} files from other formats, such as \textit{.AIF} or \textit{.MP3} using a MATLAB program
\item All audio is sampled at $44,100$ Hz and \textcolor{blue}{Bit depth needed - 16? 24?}
\item All audio has been down-mixed into mono-channel waveforms.
\end{enumerate}

@@

\begin{figure}[H]
\begin{center}
%textcolor{red}{Plot of TDE Feature Here}
\includegraphics[scale=0.3]{../FiguresFeatures/Time_Domain_Env}
\end{center}
\caption{A comparison of the Time Domain Envelope across each class using a box-and-whisker plot}
\label{fig-FeatureTDE}
\end{figure}

@@

\begin{figure}[H]
\begin{center}
%\textcolor{red}{PLOT OF ZXR FEATURES HERE}
\includegraphics[scale=0.3]{../FiguresFeatures/Zero_X-Rate}
\end{center}
\caption{A comparison of the Zero-Crossing Rate for each class using a box-and-whisker plot}
\label{fig-FeatureZXR}
\end{figure}

@@

\begin{figure}[H]
\begin{center}
%\textcolor{red}{PLOT OF TCM FEATURES HERE}
\includegraphics[scale=0.3]{../FiguresFeatures/Time_Center_of_Mass}
\end{center}
\caption{A comparison of the temporal center mass for each class using a box-and-whisker plot}
\label{fig-FeatureTCM}
\end{figure}

@@

\begin{figure}[H]
\begin{center}
%\textcolor{red}{PLOT OF ACC FEATURES HERE}

	\begin{subfigure}{1.0\textwidth}
	\centering
	\includegraphics[width=\textwidth , height=0.2\textheight]
		{../FiguresFeatures/Auto_Correlation_1}
	\caption{ACC $k=1$}
	\end{subfigure}

	\begin{subfigure}{1.0\textwidth}
	\centering
	\includegraphics[width=\textwidth , height=0.2\textheight]
		{../FiguresFeatures/Auto_Correlation_2}
	\caption{ACC $k=2$}
	\end{subfigure}

	\begin{subfigure}{1.0\textwidth}
	\centering
	\includegraphics[width=\textwidth , height=0.2\textheight]
		{../FiguresFeatures/Auto_Correlation_3}
	\caption{ACC $k=3$}
	\end{subfigure}

	\begin{subfigure}{1.0\textwidth}
	\centering
	\includegraphics[width=\textwidth , height=0.2\textheight]
		{../FiguresFeatures/Auto_Correlation_4}
	\caption{ACC $k=4$}
	\end{subfigure}

\end{center}
\caption{A comparison of the the first four auto correlation coefficents in each class using a box-and-whisker plot}
\label{fig-FeatureACC}
\end{figure}

@@

\paragraph*{}As the frequency bin index increases, the width of the bin in frequency space increases. \textcolor{red}{Finish this! What does a MFCC tell us with words!}

\begin{figure}[H]
\begin{center}
%\textcolor{red}{PLOT OF MFCC FEATURES HERE}

\begin{subfigure}{1.0\textwidth}
	\centering
	\includegraphics[width=\textwidth , height=0.2\textheight]
		{../FiguresFeatures/MFCC_1}
	\caption{MFCC $R[1]$}
	\end{subfigure}

	\begin{subfigure}{1.0\textwidth}
	\centering
	\includegraphics[width=\textwidth , height=0.2\textheight]
		{../FiguresFeatures/MFCC_4}
	\caption{MFCC $R[4]$}
	\end{subfigure}

	\begin{subfigure}{1.0\textwidth}
	\centering
	\includegraphics[width=\textwidth , height=0.2\textheight]
		{../FiguresFeatures/MFCC_8}
	\caption{MFCC $R[8]$}
	\end{subfigure}

	\begin{subfigure}{1.0\textwidth}
	\centering
	\includegraphics[width=\textwidth , height=0.2\textheight]
		{../FiguresFeatures/MFCC_12}
	\caption{MFCC $R[12]$}
	\end{subfigure}

\end{center}
\caption{A comparison of 4 Mel Frequency Cepstral Coefficients, $1$, $4$, $8$ and $12$ for each class using box-and-whisker plots}
\label{fig-FeatureMFCCs}
\end{figure}

@@

\begin{figure}[H]
\label{fig-FeatureFCM}
\begin{center}
%\textcolor{red}{PLOT OF FCM FEATURES HERE}
\includegraphics[scale=0.3]{../FiguresFeatures/Frequency_Center_of_Mass}
\end{center}
\caption{A comparison of the frequency center-of-mass for each class using box-and-whisker plots}
\end{figure}
